%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{verbatim}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% \\sans-serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
%\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% serif
%\usepackage{CormorantGaramond}
 \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.08003pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.95\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

 


\begin{center}
{\Huge \scshape  \textbf{Kumardwij Bhatnagar (Kumar)}}
\\[5pt]
\begin{tabular}{c c c c c}
\faPhone\enspace \href{tel:4709292615} {(470)-929-2615} $|$ & \enspace\faEnvelope\enspace \color{blue}\href{mailto:kumardwij.bhatnagar@gmail.com} {kumardwij.bhatnagar@gmail.com} $|$ & \enspace\faLinkedinSquare\href{https://www.linkedin.com/in/kdbhatnagar/}{\color{blue}/kdbhatnagar} $|$ & \enspace\faGithub\href{https://github.com/kdab99}{\color{blue}/kdab99} $|$ & \enspace\faHome\enspace{\textbf{USA}}
\end{tabular}
\end{center}

\begin{flushleft}
    {Dynamic professional with 3+ years of experience in \textbf{Governance, Risk, and Compliance (GRC)} and \textbf{Cloud Security}. Skilled in managing control assessments, regulatory compliance, and ensuring audit readiness for complex systems. I seek to contribute my expertise to enhance compliance processes and ensure efficient security governance. Cultivated extensive cross-cultural expertise in IT governance and compliance, as evidenced by successful project delivery in 6 countries (USA, Canada, UAE, Qatar, Saudi Arabia, India), by working with clients across 5+ diverse sectors including financial services, air navigation, utilities, power generation, and government departments. }
\end{flushleft}

\section{Skills}
 \resumeSubHeadingListStart
        \resumeSubItem{\textbf{Programming \& Scripting Languages:}}
        {Python, C, C++, Bash, PowerShell}{}
        \resumeSubItem{\textbf{Frameworks:}}
        {MITRE ATT\&CK, Cyber Killchain, ISO 27001, NIST Cybersecurity Framework, EU GDPR, PCI-DSS, FedRAMP, SOC2,  HIPAA}
        \resumeSubItem{\textbf{Tools:}}
        {OneTrust, BurpSuite, Acunetix, Nmap, Kali Linux, Git, Docker, Wireshark, Autopsy, AWS, Azure Active Directory, Windows OS, Microsoft Office }
        \resumeSubItem{\textbf{Skills:}}
        {Information Security Risk Management, Data Privacy Impact Assessment, Digital Forensics, Cloud Security, Penetration Testing, Security Operations}
    
 \resumeSubHeadingListEnd 


\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, Georgia}
      {\textbf{Master} of Science in \textbf{Cybersecurity} | GPA: \textbf{3.9/4.0}}{May 2024}
      {\textit{Specialization in the Information Security (CS) track} }
      
      {\footnotesize{Relevant coursework: Information Security Policies, Data Privacy, Data Governance, Network Security, Cloud Security}}
      
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, India}
      {\textbf{Bachelor} of Technology in \textbf{Computer Science} with specialization in \textbf{Information Security}}{June 2020}
      {\textit{Specialization in Information Security}}
  \resumeSubHeadingListEnd


\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
      {PwC}{}
      {Associate - Cybersecurity }{January 2020 - August 2022}
      \resumeItemListStart
        \resumeItem{}
          {Strengthened the infrastructure by performing Dynamic \& Static Application Penetration Testing (DAST \& SAST) for 300+ web \& mobile (Android \& iOS) applications \& Wi-Fi networks for India's leading private \& government banks.}
        \resumeItem{}
          {Performed Wi-Fi Penetration Testing in the headquarters of a large private bank and successfully spoofed 5+ access points (AP).}
       \resumeItem{}
       {Formulated a detailed \textbf{Cloud Security policy} for a \textbf{large insurance business} that streamlined access controls and monitoring processes, ensuring compliance and enhancing data security for 1M+ records during their cloud migration. } 
       \resumeItem{}
       {Led the \textbf{technical \& functional third-party vendor security assessments} for 10+ vendors for the Government of India for digital payments through feature phones. }
        \resumeItem{}
        {Conducted a top-to-bottom technical assessment of 50+ technologies that were part of the Security Operations at India's largest stock exchange.}
        \resumeItem{}
        {Assessed 20+ processes \& databases of a global insurance organization for Indian \& European Data Privacy regulations such as the GDPR \& the Indian Personal Data Privacy Bill.}
        \resumeItem{}
        {Contributed to the IT and IT Security \textbf{current state (as-is) assessment, Maturity assessment, and Target Operating Model (TOM)} for a Government Ministry in the Middle East impacting 300+ schools in the country.}
        \resumeItem{}
        {Conducted access rights review and recertification projects to analyze and finetune role-based access for a large bank in the UAE.}
        \resumeItem{}
        {Created an \textbf{Information Security Management System (ISMS) \& Information Technology Service Management Manual (ITSM)} for 10+ customers in the air navigation, education, power transmission, \& utility sectors based on frameworks such as\textbf{ ISO/IEC: 27001, NIST CSF, \& ITIL v4}.}
        \resumeItem{}
        {\textbf{Spearheaded} compliance documentation for Salesforce Asia Pacific, resulting in demonstrated adherence to 2+ major Indian regulatory frameworks (RBI and IRDAI), by authoring 3+ comprehensive white papers mapping 50+ IT general controls to cybersecurity standards.}
        \resumeItem{}
        {\textbf{Engineered} a robust governance framework for a government power transmission company, as measured by the successful implementation of 5+ international standards (ISO:27001, NIST CSF, ITIL v4, COBIT, National Information Assurance Framework), by developing a Target Operating Model, ISMS, and ITSM manual covering 100+ IT processes.}
        \resumeItem{}
        {\textbf{Pioneered} privacy compliance strategies for an insurance company's Indian subsidiary, supporting European operations' backend data center setup processing 1M+ customer records, by developing a comprehensive data classification system aligned with 3 major privacy standards (EU GDPR, Indian Personal Data Protection Act, ISO:27701).}
        \resumeItem{}
        {\textbf{Revitalized} the cybersecurity framework for a large group of financial companies, encompassing 15+ subsidiaries with a \$100B+ market cap, by conducting an exhaustive review ensuring alignment with 6 international standards (ISO:27001, ISO:27002, NIST 800:53, NIST RMF, NIST CSF, IT SOX) across 100+ control areas.}
      \resumeItemListEnd

    
    
    \resumeSubheading
          {BusPatrol}{}
          {IT Governance \& Compliance Intern}{May 2023 - August 2023}
          \resumeItemListStart
            \resumeItem{}
            {Implemented a cutting-edge machine learning algorithm to analyze and categorize client contracts using \textbf{PowerShell \& Microsoft Syntex}, resulting in a 30\% increase in accuracy compared to previous manual methods.}
            \resumeItem{}
            {Conducted penetration testing assessments on 10+ internet-facing websites for the organization, engaging with software development \& QA teams for remediation.}
            \resumeItem{}
            {Mapped the \textbf{PII and PCI architectural data flows} within the organization, identifying 10+ distinct privacy requirements, which played a pivotal role in establishing the Privacy department.}
            \resumeItem{}
            {Coordinated \& assisted the team in ensuring \textbf{annual SOC-2 \& FedRAMP compliance} and gathering evidence from departments such as Legal, Software Development, Quality Assurance, and more.}
            \resumeItem{}
            {\textbf{Orchestrated} SOC2 and FEDRAMP compliance processes, enhancing data protection across operations in 2 countries (USA and Canada), by facilitating evidence collection for 200+ control points and mapping 10+ architectural data flows for PCI and PII to ensure adherence to 3+ privacy laws (PCI-DSS, CCPA, GDPR.}
          \resumeItemListEnd
   
        
        
    
    \resumeSubheading
    {Georgia Institute of Technology}{Atlanta, GA, USA}
    {Graduate Teaching Assistant} {August 2023 - Present}

    \resumeItemListStart
        \resumeItem{}
        {Contributed to conducting office hours, testing \& deploying projects \& assisting in course preparation for 200+ undergrad \& grad students for class CS 6035 - Introduction to Information Security under \href{https://faculty.cc.gatech.edu/~genkin/}{Prof. Daniel Genkin}.}
     \resumeItemListEnd 
   \resumeSubheading
   {Georgia Institute of Technology}{}
   {Graduate Student Assistant - Data Governance \& Discovery}{September 2022 - Present}
   \resumeItemListStart
   \resumeItem{}
          {Contributed to the establishment of the data governance practice in the enterprise systems of Georgia Tech.}
        \resumeItem{}
        {Contributed to implementing \textbf{OneTrust's Privacy Management, Governance, Risk \& Compliance modules}, resulting in enhanced data protection \& streamlined compliance processes \& reducing data processing time by 30\% } 
        \resumeItem{}
          {Identified opportunities for data analysis in the data lake while working with the Business Intelligence, Data Privacy, and Cybersecurity teams.}
        \resumeItem{}
         {Investigated 50+ centralized data dashboards involving different data domains such as finance, admissions, academia, \& legacy data for data accuracy \& quality. }
        \resumeItem{}
        {\textbf{Bolstered} Georgia Tech's data governance practices, maintaining compliance with 3 major regulations (FERPA, GDPR, HIPAA), by contributing to the implementation of 4 OneTrust software modules (Policy Compliance, Privacy Management, Data Catalog, Data Discovery) across 5+ departments.}
    \resumeItemListEnd
   
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Evaluating Certificate Transparency for TLS Root Anchor Trust}}{\textit{January 2023 -- May 2023}}
          \resumeItemListStart
           \resumeItem{Researched Certificate Transparency (CT) logs, focusing on SSL/TLS certificate issuance delays.}
           \resumeItem{Utilized CertStream Python library to extract and analyze data from CT logs, calculating an average observed delay of 12,055 seconds.}
           \resumeItem{Highlighted the need to potentially reduce the maximum merge delay (MMD) of CT logs for improved system security and reliability.}
            \resumeItemListEnd
    
      
      \resumeProjectHeading
          {\textbf{Certis: Next-Gen Cloud Asset Management \& Threat Evaluation Framework} {\color{blue}[\href{https://doi.org/10.4236/jsea.2024.176026}{Publication}]}}{\textit{January 2024 -- Present}}
          \resumeItemListStart
            \resumeItem{Pioneered an advanced tool that integrates SSL certificate parsing, scanning, and JARM fingerprinting, enabling scanning of 5+ major cloud platforms including \textbf{AWS, GCP, Azure, \& Oracle}, and detection of 1000+ unique server fingerprints.}
            \resumeItem{Implemented cross-layer malicious behavior identification capabilities, enhancing anomaly detection by 40\% across network layers and reducing false positives by 30\% through AI-based learning techniques.}
            \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Information Security Home Lab}}{\textit{August 2022 -- Present}}
          \resumeItemListStart
            \resumeItem{Completed a Capture-the-flag (CTF) challenge with 10 flags for buffer overflow vulnerability \& return-oriented programming(ROP). }
            \resumeItem{Successfully exploited the log4j vulnerability in a closed client-server environment.}
            \resumeItem{Analyzed 3 malware samples in different ecosystems - Windows, Linux, \& Android using the Cuckoo tool.}
            \resumeItem{Implemented a \textbf{2-factor-based authentication} mechanism for a custom application login procedure; with functionality for registering new users, checking existing users' passwords, \& resetting passwords.}
            \resumeItem{Investigated the packet capture(pcap) files for malicious traffic for DDos, Botnet \& Web attacks using \textbf{Snort rules}. }
            \resumeItem{Analyzed the draft \textbf{American Data Protection \& Privacy Act's (ADPPA)} Duty of Loyalty to ascertain if it adequately protects US citizens' privacy online.}
            \resumeItem{Conducted a \textbf{Privacy Impact Assessment} of an EduTech mobile application, finding 3+ privacy areas of concern.}
            \resumeItemListEnd
          
    
      \resumeProjectHeading
          {\textbf{Comparing reliability of software in mobile operating systems}}{Jan 2018 -- May 2018}
          \resumeItemListStart
            \resumeItem{Conducted a comparative study on the open mobile OS (Android) with the closed mobile OS (iOS) systems based on Productivity, Processing power, Security, and frequency and cause of malfunctions}
          \resumeItemListEnd
    
    \resumeSubHeadingListEnd

\section{Courses and Certifications}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Network Security Expert Level 1 and 2 }{-- \textit{Fortinet}}}{May 2020 -- May 2022}
    \resumeProjectHeading
          {\textbf{Certified Network Security Specialist} {-- \textit{ICSI, UK}}}{May 2020 -- Present}
    \resumeProjectHeading
          {\textbf{AWS Cloud Practitioner} {-- \textit{AWS}}}{June 2020 -- Present}
          
    
    
    \resumeSubHeadingListEnd


\section{Achievements}
    \begin{tabular}{ p{3cm} | p{15cm} } 
     \small{\textbf{Sports}} \hspace{2cm}   & \hspace{1cm} \textbf{Winner} - Sub-Junior State Judo Championship \\ 
     \small{\textbf{Theatre}}              & \hspace{1cm} \textbf{Winner} - Indywood National Talent Hunt, Actor, \& Director for 20+ plays \\
     \small{\textbf{Filmmaking}}            & \hspace{1cm} Remotely directed a short film during the COVID pandemic {\href{https://www.youtube.com/watch?v=_vjI3XiFEbA}{\color{blue}{Kashmakash}}}  
    \end{tabular}


\end{document}